The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-03-22 src/ms.tex

\python is widely used by Data Central, and \astropy and its wider ecosystem
play a vital role in the initial ingestion, reduction, access and visualization
of the hosted data and services. For example, the AAT Archive hosts date back to
1974, so \astropycoordinates, \astropytime and \astropyfits are used to ingest
data flowing from the AAT to ensure that a consistent time and coordinate system
is provided to users for simpler querying.

>>>>

\python is widely used by Data Central, and \astropy and its wider ecosystem
play a vital role in the initial ingestion, reduction, access and visualization
of the hosted data and services. For example, the AAT Archive hosts data from as early as
1974, so \astropycoordinates, \astropytime and \astropyfits are used to ingest
data flowing from the AAT to ensure that a consistent time and coordinate system
is provided to users for simpler querying.
